Fluoroproj: Title to be decided later

### 2023-03-31 manuscript/manuscript_sds.qmd
added outline to intro based on Betty

The goal of this paper is to compare different handheld or in situ fluorometers with respect to a common benchmark (extracted chlorophyll and phycocyanin) in order to assess the feasibility of combining data from these various sources.

>>>>

HAB expansion is a problem and temporal nature means lots of groups have to be proactively involved in monitoring

To respond to this problem industry has developed a variety of handhelds

Taking individual fluorometer data across a region or between groups is difficult because these instruments all measure a little different

The goal of this paper is to compare different handheld or in situ fluorometers with respect to a common benchmark (extracted chlorophyll and phycocyanin) in order to provide a communications tool for groups using these different instruments.
